\normalfont\spacedallcaps{Language reclamation: Literature review}

### 2023-06-25 assignment-4/article.tex
Run linter check on assignment 4

\begin{equation*}
	L(\phi) = - \sum_j \log\left(1 - \textrm{sig}(f(g(z_j, \theta), \phi)\right) - \sum_i log\left(\textrm{sig}(f(x_i, \phi))\right)
\end{equation*}

@@

\begin{equation*}
	L(\phi) = - \sum_j \log(1 - D(\hat{x}_j, \phi)) - \sum_i log(D(x_i, \phi))
\end{equation*}

The result is a binary cross-entropy loss where the goal is to distinguish $x_i$ from $\hat{x}_i$. Real samples $x_i$ decrease the loss by $log(D(x_i, \phi))$ while generated samples increase the loss by $\log(1-D(\hat{x}_j, \phi))$.

@@

\begin{equation*}
	L(\theta) = - \sum_j \log\left(1 - \textrm{sig}(f(g(z_j, \theta), \phi)\right)
\end{equation*}

@@

If however the generator only produces a subset of the genuine images, then it is sub-optimal. This phenomenon is referred to as as "mode collapse", where the generator learns to generate only a limited variety of samples.

@@

For each $t \in T$ , let $S_t = \{x_{t,i,j}\}, i = 1, \ldots , m$ for $j \in J$ be the dataset of t-noisy images, $x_{t,i,j} = \sqrt{\alpha_t} x_i + \sqrt{1 - \alpha_t} \epsilon_j$

@@

Minimizing this loss amounts to minimizing $||g_t (x_{t,i,j})-\epsilon_j||^2$ for every $i = 1, ..., m$, and every $j \in J$.

@@

Suppose there are two different minimizers $g^t$ and $h^t$ of the loss. They both achieve the minimum loss, which is zero. So for all $i = 1, ..., m$ and for all $j \in J$,

@@

Consider transforming a uniform base density defined on $z\in[0,1]$ using the function $x = f[z] = z^2$. Find an expression for the transformed distribution $Pr(x)$.

@@

\begin{equation*}
	Pr(z) = \frac{1}{\sqrt{2\pi}} \exp \left[\frac{-z^2}{2}\right]
\end{equation*}

@@

Find an expression for the transformed distribution $Pr(x)$.

@@

As before, let $P_Z = Pr(z)$. Then $x = f[z]$ implies $z = \log(x(1-x))$, from which we derive: $\frac{dz}{dx} = \frac{1-2x}{x(1-x)}$

@@

\begin{align*}
	p_X(x) & = p_Z(z) \left|\frac{dz}{dx}\right|                                                                 \\
	       & = \frac{1}{\sqrt{2\pi}} \exp \left[-\frac{1}{2}(\log(x(1-x)))^2 \right] \cdot \frac{|1-2x|}{x(1-x)}
\end{align*}

@@

Why does it not matter if we can only evaluate the probability q(x) up to a scaling factor $\kappa$? Does the network have to be invertible to minimize this loss function? Explain your reasoning.

@@

$$z = a \cdot \epsilon_1 + b \cdot \epsilon_2$$

>>>>

\begin{equation*}
	L(\phi) = - \sum_j \log\left(1 - \textrm{sig} (f(g(z_j, \theta), \phi))\right) - \sum_i \log\left(\textrm{sig}(f(x_i, \phi))\right)
\end{equation*}

@@

\begin{equation*}
	L(\phi) = - \sum_j \log(1 - D(\hat{x}_j, \phi)) - \sum_i \log(D(x_i, \phi))
\end{equation*}

The result is a binary cross-entropy loss where the goal is to distinguish $x_i$ from $\hat{x}_i$. Real samples $x_i$ decrease the loss by $\log(D(x_i, \phi))$ while generated samples increase the loss by $\log(1-D(\hat{x}_j, \phi))$.

@@

\begin{equation*}
	L(\theta) = - \sum_j \log\left(1 - \textrm{sig}(f(g(z_j, \theta), \phi))\right)
\end{equation*}

@@

If however the generator only produces a subset of the genuine images, then it is sub-optimal. This phenomenon is referred to as `mode collapse', where the generator learns to generate only a limited variety of samples.

@@

For each $t \in T$, let $S_t = \{x_{t,i,j}\}, i = 1, \ldots , m$ for $j \in J$ be the dataset of t-noisy images, $x_{t,i,j} = \sqrt{\alpha_t} x_i + \sqrt{1 - \alpha_t} \epsilon_j$

@@

Minimizing this loss amounts to minimizing $||g_t (x_{t,i,j})-\epsilon_j||^2$ for every $i = 1, \ldots, m$, and every $j \in J$.

@@

Suppose there are two different minimizers $g^t$ and $h^t$ of the loss. They both achieve the minimum loss, which is zero. So for all $i = 1, \ldots, m$ and for all $j \in J$,

@@

Consider transforming a uniform base density defined on $z\in[0,1]$ using the function $x = f[z] = z^2$. Find an expression for the transformed distribution $\Pr(x)$.

@@

\begin{equation*}
	\Pr(z) = \frac{1}{\sqrt{2\pi}} \exp \left[\frac{-z^2}{2}\right]
\end{equation*}

@@

Find an expression for the transformed distribution $\Pr(x)$.

@@

As before, let $P_Z = \Pr(z)$. Then $x = f[z]$ implies $z = \log(x(1-x))$, from which we derive: $\frac{dz}{dx} = \frac{1-2x}{x(1-x)}$

@@

\begin{align*}
	p_X(x) & = p_Z(z) \left|\frac{dz}{dx}\right|                                                                   \\
	       & = \frac{1}{\sqrt{2\pi}} \exp \left[-\frac{1}{2}{(\log(x(1-x)))}^2 \right] \cdot \frac{|1-2x|}{x(1-x)}
\end{align*}

@@

Why does it not matter if we can only evaluate the probability $q(x)$ up to a scaling factor $\kappa$? Does the network have to be invertible to minimize this loss function? Explain your reasoning.

@@

\[z = a \cdot \epsilon_1 + b \cdot \epsilon_2\]
